Arrangement for DroneGo

### 2020-03-09 PAPER.tex
Updates from Overleaf

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
     \vspace{5pt}
     \textbf{Keywords}: Drone, Route Planning, 3D Bin-Packing, AHP.

@@

    $c_0$    & The initial CO^2 concentration(in 1850) \\
    $F(t)$  & radiative forcing in year t \\
    $a_0,b$  & \textcolor[rgb]{ .133,  .133,  .133}{Constant coefficient} \\
    $T(t)$  & \textcolor[rgb]{ .2,  .2,  .2}{Temperature in year t} \\
    $\beta$  & Specific heat capacity \\
    $\gamma$ & heat capacity ratio  \\
    $\kappa$ & \multicolumn{1}{p{25.555em}}{thermal diffusion coefficient of ocean} \\
    $LCI$   & Liveable Country Index \\
    $NRI$   & \textcolor[rgb]{ .133,  .133,  .133}{National Responsibility Index} \\
    $IRI$   & International Responsibility Index \\
    \toprule
    \end{tabular}%
  \label{Notations}%
\end{table}%

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture site.png}
	\caption{ flow diagram of solution}\label{culture site}
\end{figure}

@@

%7.1
\subsection{Liveable Country Index (LCI)}
We selected population density, per capita GDP, per capita freshwater resources, and per capita arable land as indicators to measure the country's settable index. The higher the emigration index, the more able countries are to receive EDPs.

@@

%7.2
\subsection{National Responsibility Index (NRI)}
First, we select per capita CO2 emissions and per capita energy consumption as indicators of the National Responsibility Index, because the greenhouse effect is the leading cause of sea-level rise. The higher the National Responsibility Index, the more responsible a country is to accept EDPs.

After that, we normalize per capita $CO^2$ emissionss and per capita energy consumption of countries with LCI value greater than 0, and measure their contribution to the National Responsibility Index with a weighting of 50\% each. The corresponding NRI of 57 countries was obtained. The results are shown in figure \ref{NRI}.

@@

The island nations at risk are scattered across the world's oceans. The influence of geography on resettlement must be taken into account when considering the problem of EDPs. Therefore, we regard the distance between island countries and countries with high IRI as one of the factors determining our policy.

@@

%-------------------------------------8
\section{Policies for Protection of Human Rights}

>>>>

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
     \vspace{5pt}
     \textbf{Keywords}: Sea-level Rise, EDPs , 3D Bin-Packing, Factor Analysis.

@@

    $c_0$    & The initial CO$_2$ concentration(in 1850) \\
    $F(t)$  & radiative forcing in year t \\
    $a_0,b$  & \textcolor[rgb]{ .133,  .133,  .133}{Constant coefficient} \\
    $T(t)$  & \textcolor[rgb]{ .2,  .2,  .2}{Temperature in year t} \\
    $\beta$  & Specific heat capacity \\
    $\gamma$ & heat capacity ratio  \\
    $\kappa$ & \multicolumn{1}{p{25.555em}}{thermal diffusion coefficient of ocean} \\
    $LCI$   & Liveable Country Index \\
    $NRI$   & \textcolor[rgb]{ .133,  .133,  .133}{National Responsibility Index} \\
    $IRI$   & International Responsibility Index \\
    \toprule
    \end{tabular}%
  \label{Notations}%
\end{table}%

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture site.png}
	\caption{ World Heritage}\label{culture site}
\end{figure}

@@

%7.1
\subsection{Liveable Country Index (LCI)}
A person cannot survive without land, property, freshwater, and food. The premise for a country to accept EDPs is to guarantee fundamental human rights, such as the right to life, land, work, and freshwater. So we selected population density, per capita GDP, per capita freshwater resources, and per capita arable land as indicators to measure the country's settable index. The higher the Liveable Country Index, the better the country can guarantee the human rights of EDPs.

@@

%7.2
\subsection{National Responsibility Index (NRI)}
First, we select per capita CO$_2$ emissions and per capita energy consumption as indicators of the National Responsibility Index, because the greenhouse effect is the leading cause of sea-level rise. The higher the National Responsibility Index, the more responsible a country is to accept EDPs.

After that, we normalize per capita CO$_2$ emissionss and per capita energy consumption of countries with LCI value greater than 0, and measure their contribution to the National Responsibility Index with a weighting of 50\% each. The corresponding NRI of 57 countries was obtained. The results are shown in figure \ref{NRI}.

@@

The island nations at risk are scattered across the world's oceans. Long-distance migration is not only expensive but also inefficient; thus, the influence of geography on resettlement must be taken into account when considering the problem of EDPs. Therefore, we regard the distance between island countries and countries with high IRI as one of the factors determining our policy.

@@

%-------------------------------------8
\section{Migration Policy Based on Protection of Human Rights}
